{\scriptsize
\begin{longtable}{p{3cm}p{6cm}p{7cm}rrrp{3cm}r}
\caption{Articles from bibtex (Total 167)}\\ \toprule
Key& Authors & Title & LC & Cite & Year & Journal & Pages \\ \midrule\endhead
\bottomrule
\endfoot
PrataAN23 \href{https://www.sciencedirect.com/science/article/pii/S2666720723001522}{PrataAN23} & Bruno A. Prata, Levi R. Abreu, Marcelo S. Nagano & Applications of constraint programming in production scheduling problems: A descriptive bibliometric analysis & \href{articles/PrataAN23.pdf}{Yes} & \cite{PrataAN23} & 2024 & Results in Control and Optimization & 17\\
abs-2402-00459 \href{https://doi.org/10.48550/arXiv.2402.00459}{abs-2402-00459} & S. Nguyen, Dhananjay R. Thiruvady, Y. Sun, M. Zhang & Genetic-based Constraint Programming for Resource Constrained Job Scheduling & \href{articles/abs-2402-00459.pdf}{Yes} & \cite{abs-2402-00459} & 2024 & CoRR & 21\\
AbreuNP23 \href{https://doi.org/10.1080/00207543.2022.2154404}{AbreuNP23} & Levi Ribeiro de Abreu, Marcelo Seido Nagano, Bruno A. Prata & A new two-stage constraint programming approach for open shop scheduling problem with machine blocking & No & \cite{AbreuNP23} & 2023 & Int. J. Prod. Res. & 20\\
AkramNHRSA23 \href{https://doi.org/10.1109/ACCESS.2023.3343409}{AkramNHRSA23} & Bilal Omar Akram, Nor Kamariah Noordin, F. Hashim, Mohd Fadlee A. Rasid, Mustafa Ismael Salman, Abdulrahman M. Abdulghani & Joint Scheduling and Routing Optimization for Deterministic Hybrid Traffic in Time-Sensitive Networks Using Constraint Programming & \href{articles/AkramNHRSA23.pdf}{Yes} & \cite{AkramNHRSA23} & 2023 & {IEEE} Access & 16\\
AlfieriGPS23 \href{https://www.sciencedirect.com/science/article/pii/S0360835223000074}{AlfieriGPS23} & A. Alfieri, M. Garraffa, E. Pastore, F. Salassa & Permutation flowshop problems minimizing core waiting time and core idle time & \href{articles/AlfieriGPS23.pdf}{Yes} & \cite{AlfieriGPS23} & 2023 & Computers and Industrial Engineering & 13\\
Caballero23 \href{https://doi.org/10.1007/s10601-023-09357-0}{Caballero23} & Jordi Coll Caballero & Scheduling through logic-based tools & \href{articles/Caballero23.pdf}{Yes} & \cite{Caballero23} & 2023 & Constraints An Int. J. & 1\\
CzerniachowskaWZ23 \href{https://doi.org/10.12913/22998624/166588}{CzerniachowskaWZ23} & C. Kateryna, W. Radosław, Żywicki, Krzysztof & Constraint Programming for Flexible Flow Shop Scheduling Problem with Repeated Jobs and Repeated Operations & \href{articles/CzerniachowskaWZ23.pdf}{Yes} & \cite{CzerniachowskaWZ23} & 2023 & Advances in Science and Technology Research Journal & 14\\
GurPAE23 \href{https://doi.org/10.1007/s10100-022-00835-z}{GurPAE23} & S. G{\"{u}}r, M. Pinarbasi, Haci Mehmet Alakas, T. Eren & Operating room scheduling with surgical team: a new approach with constraint programming and goal programming & \href{articles/GurPAE23.pdf}{Yes} & \cite{GurPAE23} & 2023 & Central Eur. J. Oper. Res. & 25\\
IsikYA23 \href{https://doi.org/10.1007/s00500-023-09086-9}{IsikYA23} & Ey{\"{u}}p Ensar Isik, Seyda Topaloglu Yildiz, {\"{O}}zge Satir Akpunar & Constraint programming models for the hybrid flow shop scheduling problem and its extensions & \href{articles/IsikYA23.pdf}{Yes} & \cite{IsikYA23} & 2023 & Soft Comput. & 28\\
LacknerMMWW23 \href{https://doi.org/10.1007/s10601-023-09347-2}{LacknerMMWW23} & M. Lackner, C. Mrkvicka, N. Musliu, D. Walkiewicz, F. Winter & Exact methods for the Oven Scheduling Problem & \href{articles/LacknerMMWW23.pdf}{Yes} & \cite{LacknerMMWW23} & 2023 & Constraints An Int. J. & 42\\
MontemanniD23 \href{https://doi.org/10.3390/a16010040}{MontemanniD23} & R. Montemanni, M. Dell'Amico & Solving the Parallel Drone Scheduling Traveling Salesman Problem via Constraint Programming & \href{articles/MontemanniD23.pdf}{Yes} & \cite{MontemanniD23} & 2023 & Algorithms & 13\\
MontemanniD23a \href{https://doi.org/10.1016/j.ejco.2023.100078}{MontemanniD23a} & R. Montemanni, M. Dell'Amico & Constraint programming models for the parallel drone scheduling vehicle routing problem & \href{articles/MontemanniD23a.pdf}{Yes} & \cite{MontemanniD23a} & 2023 & {EURO} J. Comput. Optim. & 20\\
NaderiRR23 \href{https://doi.org/10.1287/ijoc.2023.1287}{NaderiRR23} & N. Bahman, R. Rub\'{e}n, R. Vahid & Mixed-Integer Programming vs. Constraint Programming for Shop Scheduling Problems: New Results and Outlook & \href{articles/NaderiRR23.pdf}{Yes} & \cite{NaderiRR23} & 2023 & INFORMS Journal on Computing & 27\\
ShaikhK23 \href{https://doi.org/10.1504/IJESDF.2023.10045616}{ShaikhK23} & Aftab Ahmed Shaikh, Abdullah Ayub Khan & Management of electronic ledger: a constraint programming approach for solving curricula scheduling problems & No & \cite{ShaikhK23} & 2023 & Int. J. Electron. Secur. Digit. Forensics & 12\\
YuraszeckMCCR23 \href{https://doi.org/10.1109/ACCESS.2023.3345793}{YuraszeckMCCR23} & F. Yuraszeck, E. Montero, D. Canut{-}de{-}Bon, N. Cuneo, M. Rojel & A Constraint Programming Formulation of the Multi-Mode Resource-Constrained Project Scheduling Problem for the Flexible Job Shop Scheduling Problem & \href{articles/YuraszeckMCCR23.pdf}{Yes} & \cite{YuraszeckMCCR23} & 2023 & {IEEE} Access & 11\\
abs-2305-19888 \href{https://doi.org/10.48550/arXiv.2305.19888}{abs-2305-19888} & V. Heinz, A. Nov{\'{a}}k, M. Vlk, Z. Hanz{\'{a}}lek & Constraint Programming and Constructive Heuristics for Parallel Machine Scheduling with Sequence-Dependent Setups and Common Servers & \href{articles/abs-2305-19888.pdf}{Yes} & \cite{abs-2305-19888} & 2023 & CoRR & 42\\
abs-2306-05747 \href{https://doi.org/10.48550/arXiv.2306.05747}{abs-2306-05747} & P. Tassel, M. Gebser, K. Schekotihin & An End-to-End Reinforcement Learning Approach for Job-Shop Scheduling Problems Based on Constraint Programming & \href{articles/abs-2306-05747.pdf}{Yes} & \cite{abs-2306-05747} & 2023 & CoRR & 9\\
abs-2312-13682 \href{https://doi.org/10.48550/arXiv.2312.13682}{abs-2312-13682} & G. Perez, G. Glorian, W. Suijlen, A. Lallouet & A Constraint Programming Model for Scheduling the Unloading of Trains in Ports: Extended & \href{articles/abs-2312-13682.pdf}{Yes} & \cite{abs-2312-13682} & 2023 & CoRR & 20\\
AbreuN22 \href{https://doi.org/10.1016/j.cie.2022.108128}{AbreuN22} & Levi Ribeiro de Abreu, Marcelo Seido Nagano & A new hybridization of adaptive large neighborhood search with constraint programming for open shop scheduling with sequence-dependent setup times & \href{articles/AbreuN22.pdf}{Yes} & \cite{AbreuN22} & 2022 & Comput. Ind. Eng. & 20\\
BourreauGGLT22 \href{https://doi.org/10.1080/00207543.2020.1856436}{BourreauGGLT22} & E. Bourreau, T. Garaix, M. Gondran, P. Lacomme, N. Tchernev & A constraint-programming based decomposition method for the Generalised Workforce Scheduling and Routing Problem {(GWSRP)} & \href{articles/BourreauGGLT22.pdf}{Yes} & \cite{BourreauGGLT22} & 2022 & Int. J. Prod. Res. & 19\\
CampeauG22 \href{https://doi.org/10.1007/s10601-022-09337-w}{CampeauG22} & L. Campeau, M. Gamache & Short- and medium-term optimization of underground mine planning using constraint programming & \href{articles/CampeauG22.pdf}{Yes} & \cite{CampeauG22} & 2022 & Constraints An Int. J. & 18\\
ColT22 \href{https://api.semanticscholar.org/CorpusID:251551160}{ColT22} & Giacomo Da Col, Erich Christian Teppan & Industrial-size job shop scheduling with constraint programming & \href{articles/ColT22.pdf}{Yes} & \cite{ColT22} & 2022 & Operations Research Perspectives & 19\\
FarsiTM22 \href{https://api.semanticscholar.org/CorpusID:250301745}{FarsiTM22} & A. Farsi, S. Ali Torabi, M. Mokhtarzadeh & Integrated surgery scheduling by constraint programming and meta-heuristics & No & \cite{FarsiTM22} & 2022 & International Journal of Management Science and Engineering Management & null\\
Fatemi-AnarakiMFN22 \href{https://api.semanticscholar.org/CorpusID:252524295}{Fatemi-AnarakiMFN22} & S. Fatemi-Anaraki, R. Tavakkoli-Moghaddam, M. Foumani, B. Vahedi-Nouri & Scheduling of Multi-Robot Job Shop Systems in Dynamic Environments: Mixed-Integer Linear Programming and Constraint Programming Approaches & No & \cite{Fatemi-AnarakiMFN22} & 2022 & Omega & null\\
FetgoD22 \href{https://doi.org/10.1007/s43069-022-00172-6}{FetgoD22} & S{\'{e}}v{\'{e}}rine Betmbe Fetgo, Cl{\'{e}}mentin Tayou Djam{\'{e}}gni & Horizontally Elastic Edge-Finder Algorithm for Cumulative Resource Constraint Revisited & \href{articles/FetgoD22.pdf}{Yes} & \cite{FetgoD22} & 2022 & Oper. Res. Forum & 32\\
HeinzNVH22 \href{https://doi.org/10.1016/j.cie.2022.108586}{HeinzNVH22} & V. Heinz, A. Nov{\'{a}}k, M. Vlk, Z. Hanz{\'{a}}lek & Constraint Programming and constructive heuristics for parallel machine scheduling with sequence-dependent setups and common servers & \href{articles/HeinzNVH22.pdf}{Yes} & \cite{HeinzNVH22} & 2022 & Comput. Ind. Eng. & 16\\
MullerMKP22 \href{https://doi.org/10.1016/j.ejor.2022.01.034}{MullerMKP22} & D. M{\"{u}}ller, Marcus Gerhard M{\"{u}}ller, D. Kress, E. Pesch & An algorithm selection approach for the flexible job shop scheduling problem: Choosing constraint programming solvers through machine learning & \href{articles/MullerMKP22.pdf}{Yes} & \cite{MullerMKP22} & 2022 & Eur. J. Oper. Res. & 18\\
PohlAK22 \href{https://doi.org/10.1016/j.ejor.2021.08.028}{PohlAK22} & M. Pohl, C. Artigues, R. Kolisch & Solving the time-discrete winter runway scheduling problem: {A} column generation and constraint programming approach & \href{articles/PohlAK22.pdf}{Yes} & \cite{PohlAK22} & 2022 & Eur. J. Oper. Res. & 16\\
ShiYXQ22 \href{https://doi.org/10.1080/00207543.2021.1963496}{ShiYXQ22} & G. Shi, Z. Yang, Y. Xu, Y. Quan & Solving the integrated process planning and scheduling problem using an enhanced constraint programming-based approach & No & \cite{ShiYXQ22} & 2022 & Int. J. Prod. Res. & 18\\
SubulanC22 \href{https://doi.org/10.1007/s00500-021-06399-5}{SubulanC22} & K. Subulan, G. {\c{C}}akir & Constraint programming-based transformation approach for a mixed fuzzy-stochastic resource investment project scheduling problem & \href{articles/SubulanC22.pdf}{Yes} & \cite{SubulanC22} & 2022 & Soft Comput. & 38\\
YunusogluY22 \href{https://doi.org/10.1080/00207543.2021.1885068}{YunusogluY22} & P. Yunusoglu, Seyda Topaloglu Yildiz & Constraint programming approach for multi-resource-constrained unrelated parallel machine scheduling problem with sequence-dependent setup times & No & \cite{YunusogluY22} & 2022 & Int. J. Prod. Res. & 18\\
YuraszeckMPV22 \href{https://api.semanticscholar.org/CorpusID:246320449}{YuraszeckMPV22} & F. Yuraszeck, G. Mej{\'i}a, J. Pereira, M. Vil{\`a} & A Novel Constraint Programming Decomposition Approach for the Total Flow Time Fixed Group Shop Scheduling Problem & \href{articles/YuraszeckMPV22.pdf}{Yes} & \cite{YuraszeckMPV22} & 2022 & Mathematics & 26\\
abs-2211-14492 \href{https://doi.org/10.48550/arXiv.2211.14492}{abs-2211-14492} & Y. Sun, S. Nguyen, Dhananjay R. Thiruvady, X. Li, Andreas T. Ernst, U. Aickelin & Enhancing Constraint Programming via Supervised Learning for Job Shop Scheduling & \href{articles/abs-2211-14492.pdf}{Yes} & \cite{abs-2211-14492} & 2022 & CoRR & 17\\
AbohashimaEG21 \href{https://doi.org/10.1109/ACCESS.2021.3112600}{AbohashimaEG21} & H. Abohashima, Amr B. Eltawil, Mohamed S. Gheith & A Mathematical Programming Model and a Firefly-Based Heuristic for Real-Time Traffic Signal Scheduling With Physical Constraints & \href{articles/AbohashimaEG21.pdf}{Yes} & \cite{AbohashimaEG21} & 2021 & {IEEE} Access & 14\\
AbreuAPNM21 \href{https://api.semanticscholar.org/CorpusID:238794651}{AbreuAPNM21} & Levi Ribeiro de Abreu, Kennedy A. G. Ara{\'u}jo, Bruno de Athayde Prata, Marcelo Seido Nagano, J. V. Moccellin & A new variable neighbourhood search with a constraint programming search strategy for the open shop scheduling problem with operation repetitions & No & \cite{AbreuAPNM21} & 2021 & Engineering Optimization & null\\
Bedhief21 \href{https://api.semanticscholar.org/CorpusID:240611192}{Bedhief21} & Asma Ouled Bedhief & Comparing Mixed-Integer Programming and Constraint Programming Models for the Hybrid Flow Shop Scheduling Problem with Dedicated Machines & \href{articles/Bedhief21.pdf}{Yes} & \cite{Bedhief21} & 2021 & Journal Europ{\'e}en des Syst{\`e}mes Automatis{\'e}s & 7\\
FanXG21 \href{https://doi.org/10.1016/j.cor.2021.105401}{FanXG21} & H. Fan, H. Xiong, M. Goh & Genetic programming-based hyper-heuristic approach for solving dynamic job shop scheduling problem with extended technical precedence constraints & \href{articles/FanXG21.pdf}{Yes} & \cite{FanXG21} & 2021 & Comput. Oper. Res. & 15\\
HamPK21 \href{https://api.semanticscholar.org/CorpusID:237898414}{HamPK21} & A. Ham, M. Park, Kyung Min Kim & Energy-Aware Flexible Job Shop Scheduling Using Mixed Integer Programming and Constraint Programming & \href{articles/HamPK21.pdf}{Yes} & \cite{HamPK21} & 2021 & Mathematical Problems in Engineering & 12\\
HubnerGSV21 \href{https://doi.org/10.1007/s10951-021-00682-x}{HubnerGSV21} & F. H{\"{u}}bner, P. Gerhards, C. St{\"{u}}rck, R. Volk & Solving the nuclear dismantling project scheduling problem by combining mixed-integer and constraint programming techniques and metaheuristics & \href{articles/HubnerGSV21.pdf}{Yes} & \cite{HubnerGSV21} & 2021 & J. Sched. & 22\\
KoehlerBFFHPSSS21 \href{https://doi.org/10.1007/s10601-021-09321-w}{KoehlerBFFHPSSS21} & J. Koehler, J. B{\"{u}}rgler, U. Fontana, E. Fux, Florian A. Herzog, M. Pouly, S. Saller, A. Salyaeva, P. Scheiblechner, K. Waelti & Cable tree wiring - benchmarking solvers on a real-world scheduling problem with a variety of precedence constraints & \href{articles/KoehlerBFFHPSSS21.pdf}{Yes} & \cite{KoehlerBFFHPSSS21} & 2021 & Constraints An Int. J. & 51\\
PandeyS21a \href{https://doi.org/10.1007/s11227-020-03516-3}{PandeyS21a} & V. Pandey, P. Saini & Constraint programming versus heuristic approach to MapReduce scheduling problem in Hadoop {YARN} for energy minimization & \href{articles/PandeyS21a.pdf}{Yes} & \cite{PandeyS21a} & 2021 & J. Supercomput. & 29\\
QinWSLS21 \href{https://doi.org/10.1109/TASE.2019.2947398}{QinWSLS21} & M. Qin, R. Wang, Z. Shi, L. Liu, L. Shi & A Genetic Programming-Based Scheduling Approach for Hybrid Flow Shop With a Batch Processor and Waiting Time Constraint & \href{articles/QinWSLS21.pdf}{Yes} & \cite{QinWSLS21} & 2021 & {IEEE} Trans Autom. Sci. Eng. & 12\\
VlkHT21 \href{https://doi.org/10.1016/j.cie.2021.107317}{VlkHT21} & M. Vlk, Z. Hanz{\'{a}}lek, S. Tang & Constraint programming approaches to joint routing and scheduling in time-sensitive networks & \href{articles/VlkHT21.pdf}{Yes} & \cite{VlkHT21} & 2021 & Comput. Ind. Eng. & 14\\
ZhangYW21 \href{https://doi.org/10.1016/j.cor.2021.105282}{ZhangYW21} & L. Zhang, C. Yu, T. N. Wong & A graph-based constraint programming approach for the integrated process planning and scheduling problem & \href{articles/ZhangYW21.pdf}{Yes} & \cite{ZhangYW21} & 2021 & Comput. Oper. Res. & 10\\
AlizdehS20 \href{https://doi.org/10.1504/IJAIP.2020.106687}{AlizdehS20} & S. Alizdeh, S. Saeidi & Fuzzy project scheduling with critical path including risk and resource constraints using linear programming & No & \cite{AlizdehS20} & 2020 & Int. J. Adv. Intell. Paradigms & 14\\
AstrandJZ20 \href{https://doi.org/10.1016/j.cor.2020.105036}{AstrandJZ20} & M. {\AA}strand, M. Johansson, A. Zanarini & Underground mine scheduling of mobile machines using Constraint Programming and Large Neighborhood Search & \href{articles/AstrandJZ20.pdf}{Yes} & \cite{AstrandJZ20} & 2020 & Comput. Oper. Res. & 13\\
BadicaBI20 \href{https://doi.org/10.3233/AIC-200650}{BadicaBI20} & A. Badica, C. Badica, M. Ivanovic & Block structured scheduling using constraint logic programming & No & \cite{BadicaBI20} & 2020 & {AI} Commun. & 17\\
BenediktMH20 \href{https://doi.org/10.1007/s10601-020-09317-y}{BenediktMH20} & O. Benedikt, I. M{\'{o}}dos, Z. Hanz{\'{a}}lek & Power of pre-processing: production scheduling with variable energy pricing and power-saving states & \href{articles/BenediktMH20.pdf}{Yes} & \cite{BenediktMH20} & 2020 & Constraints An Int. J. & 19\\
FallahiAC20 \href{https://api.semanticscholar.org/CorpusID:213449737}{FallahiAC20} & Abdellah El Fallahi, El Yaakoubi Anass, M. Cherkaoui & Tabu search and constraint programming-based approach for a real scheduling and routing problem & No & \cite{FallahiAC20} & 2020 & International Journal of Applied Management Science & null\\
LunardiBLRV20 \href{https://doi.org/10.1016/j.cor.2020.105020}{LunardiBLRV20} & Willian T. Lunardi, Ernesto G. Birgin, P. Laborie, D{\'{e}}bora P. Ronconi, H. Voos & Mixed Integer linear programming and constraint programming models for the online printing shop scheduling problem & \href{articles/LunardiBLRV20.pdf}{Yes} & \cite{LunardiBLRV20} & 2020 & Comput. Oper. Res. & 20\\
MengZRZL20 \href{https://doi.org/10.1016/j.cie.2020.106347}{MengZRZL20} & L. Meng, C. Zhang, Y. Ren, B. Zhang, C. Lv & Mixed-integer linear programming and constraint programming formulations for solving distributed flexible job shop scheduling problem & \href{articles/MengZRZL20.pdf}{Yes} & \cite{MengZRZL20} & 2020 & Comput. Ind. Eng. & 13\\
MokhtarzadehTNF20 \href{https://doi.org/10.1080/0951192X.2020.1736713}{MokhtarzadehTNF20} & M. Mokhtarzadeh, R. Tavakkoli{-}Moghaddam, Behdin Vahedi Nouri, A. Farsi & Scheduling of human-robot collaboration in assembly of printed circuit boards: a constraint programming approach & No & \cite{MokhtarzadehTNF20} & 2020 & Int. J. Comput. Integr. Manuf. & 14\\
Polo-MejiaALB20 \href{https://doi.org/10.1080/00207543.2019.1693654}{Polo-MejiaALB20} & O. Polo{-}Mej{\'{\i}}a, C. Artigues, P. Lopez, V. Basini & Mixed-integer/linear and constraint programming approaches for activity scheduling in a nuclear research facility & No & \cite{Polo-MejiaALB20} & 2020 & Int. J. Prod. Res. & 18\\
QinDCS20 \href{https://doi.org/10.1016/j.ejor.2020.02.021}{QinDCS20} & T. Qin, Y. Du, Jiang Hang Chen, M. Sha & Combining mixed integer programming and constraint programming to solve the integrated scheduling problem of container handling operations of a single vessel & \href{articles/QinDCS20.pdf}{Yes} & \cite{QinDCS20} & 2020 & Eur. J. Oper. Res. & 18\\
SacramentoSP20 \href{https://doi.org/10.1007/s43069-020-00036-x}{SacramentoSP20} & D. Sacramento, C. Solnon, D. Pisinger & Constraint Programming and Local Search Heuristic: a Matheuristic Approach for Routing and Scheduling Feeder Vessels in Multi-terminal Ports & \href{articles/SacramentoSP20.pdf}{Yes} & \cite{SacramentoSP20} & 2020 & Oper. Res. Forum & 33\\
WallaceY20 \href{https://doi.org/10.1007/s10601-020-09316-z}{WallaceY20} & M. Wallace, N. Yorke{-}Smith & A new constraint programming model and solving for the cyclic hoist scheduling problem & \href{articles/WallaceY20.pdf}{Yes} & \cite{WallaceY20} & 2020 & Constraints An Int. J. & 19\\
ZouZ20 \href{https://api.semanticscholar.org/CorpusID:208840808}{ZouZ20} & X. Zou, L. Zhang & A constraint programming approach for scheduling repetitive projects with atypical activities considering soft logic & No & \cite{ZouZ20} & 2020 & Automation in Construction & 1\\
EscobetPQPRA19 \href{https://doi.org/10.1016/j.compchemeng.2018.08.040}{EscobetPQPRA19} & T. Escobet, V. Puig, J. Quevedo, P. Pal{\`{a}}{-}Sch{\"{o}}nw{\"{a}}lder, J. Romera, W. Adelman & Optimal batch scheduling of a multiproduct dairy process using a combined optimization/constraint programming approach & \href{articles/EscobetPQPRA19.pdf}{Yes} & \cite{EscobetPQPRA19} & 2019 & Comput. Chem. Eng. & 10\\
GurEA19 \href{https://api.semanticscholar.org/CorpusID:88492001}{GurEA19} & Şeyda G{\"u}r, T. Eren, Hacı Mehmet Alakaş & Surgical Operation Scheduling with Goal Programming and Constraint Programming: A Case Study & \href{articles/GurEA19.pdf}{Yes} & \cite{GurEA19} & 2019 & Mathematics & 24\\
HauderBRPA19 \href{https://api.semanticscholar.org/CorpusID:67855609}{HauderBRPA19} & Viktoria A. Hauder, A. Beham, S. Raggl, Sophie N. Parragh, M. Affenzeller & On constraint programming for a new flexible project scheduling problem with resource constraints & \href{articles/HauderBRPA19.pdf}{Yes} & \cite{HauderBRPA19} & 2019 & ArXiv & 62\\
NishikawaSTT19 \href{http://www.ijnc.org/index.php/ijnc/article/view/201}{NishikawaSTT19} & H. Nishikawa, K. Shimada, I. Taniguchi, H. Tomiyama & A Constraint Programming Approach to Scheduling of Malleable Tasks & No & \cite{NishikawaSTT19} & 2019 & Int. J. Netw. Comput. & 16\\
Novas19 \href{https://doi.org/10.1016/j.cie.2019.07.011}{Novas19} & Juan M. Novas & Production scheduling and lot streaming at flexible job-shops environments using constraint programming & \href{articles/Novas19.pdf}{Yes} & \cite{Novas19} & 2019 & Comput. Ind. Eng. & 13\\
WikarekS19 \href{https://doi.org/10.1142/S2196888819500027}{WikarekS19} & J. Wikarek, P. Sitek & A Constraint-Based Declarative Programming Framework for Scheduling and Resource Allocation Problems & \href{articles/WikarekS19.pdf}{Yes} & \cite{WikarekS19} & 2019 & Vietnam. J. Comput. Sci. & 22\\
YounespourAKE19 \href{https://api.semanticscholar.org/CorpusID:208103305}{YounespourAKE19} & M. Younespour, A. Atighehchian, K. Kianfar, Ehsan Tarkesh Esfahani & Using mixed integer programming and constraint programming for operating rooms scheduling with modified block strategy & No & \cite{YounespourAKE19} & 2019 & Operations research for health care & 1\\
abs-1901-07914 \href{http://arxiv.org/abs/1901.07914}{abs-1901-07914} & Jan Kristof Behrens, R. Lange, M. Mansouri & A Constraint Programming Approach to Simultaneous Task Allocation and Motion Scheduling for Industrial Dual-Arm Manipulation Tasks & \href{articles/abs-1901-07914.pdf}{Yes} & \cite{abs-1901-07914} & 2019 & CoRR & 8\\
abs-1902-01193 \href{http://arxiv.org/abs/1902.01193}{abs-1902-01193} & O. M. Alade, A. O. Amusat & Solving Nurse Scheduling Problem Using Constraint Programming Technique & \href{articles/abs-1902-01193.pdf}{Yes} & \cite{abs-1902-01193} & 2019 & CoRR & 9\\
abs-1902-09244 \href{http://arxiv.org/abs/1902.09244}{abs-1902-09244} & Viktoria A. Hauder, A. Beham, S. Raggl, Sophie N. Parragh, M. Affenzeller & On constraint programming for a new flexible project scheduling problem with resource constraints & \href{articles/abs-1902-09244.pdf}{Yes} & \cite{abs-1902-09244} & 2019 & CoRR & 62\\
abs-1911-04766 \href{http://arxiv.org/abs/1911.04766}{abs-1911-04766} & T. Geibinger, F. Mischek, N. Musliu & Investigating Constraint Programming and Hybrid Methods for Real World Industrial Test Laboratory Scheduling & \href{articles/abs-1911-04766.pdf}{Yes} & \cite{abs-1911-04766} & 2019 & CoRR & 16\\
BaptisteB18 \href{https://doi.org/10.1016/j.dam.2017.05.001}{BaptisteB18} & P. Baptiste, N. Bonifas & Redundant cumulative constraints to compute preemptive bounds & \href{articles/BaptisteB18.pdf}{Yes} & \cite{BaptisteB18} & 2018 & Discret. Appl. Math. & 10\\
BorghesiBLMB18 \href{https://doi.org/10.1016/j.suscom.2018.05.007}{BorghesiBLMB18} & A. Borghesi, A. Bartolini, M. Lombardi, M. Milano, L. Benini & Scheduling-based power capping in high performance computing systems & \href{articles/BorghesiBLMB18.pdf}{Yes} & \cite{BorghesiBLMB18} & 2018 & Sustain. Comput. Informatics Syst. & 13\\
FahimiOQ18 \href{https://doi.org/10.1007/s10601-018-9282-9}{FahimiOQ18} & H. Fahimi, Y. Ouellet, C. Quimper & Linear-time filtering algorithms for the disjunctive constraint and a quadratic filtering algorithm for the cumulative not-first not-last & \href{articles/FahimiOQ18.pdf}{Yes} & \cite{FahimiOQ18} & 2018 & Constraints An Int. J. & 22\\
GedikKEK18 \href{https://doi.org/10.1016/j.cie.2018.05.014}{GedikKEK18} & R. Gedik, D. Kalathia, G. Egilmez, E. Kirac & A constraint programming approach for solving unrelated parallel machine scheduling problem & \href{articles/GedikKEK18.pdf}{Yes} & \cite{GedikKEK18} & 2018 & Comput. Ind. Eng. & 11\\
GokgurHO18 \href{https://doi.org/10.1080/00207543.2017.1421781}{GokgurHO18} & B. G{\"{o}}kg{\"{u}}r, B. Hnich, S. {\"{O}}zpeynirci & Parallel machine scheduling with tool loading: a constraint programming approach & No & \cite{GokgurHO18} & 2018 & Int. J. Prod. Res. & 17\\
Ham18 \href{https://api.semanticscholar.org/CorpusID:116853255}{Ham18} & A. Ham & Integrated scheduling of m-truck, m-drone, and m-depot constrained by time-window, drop-pickup, and m-visit using constraint programming & No & \cite{Ham18} & 2018 & Transportation Research Part C: Emerging Technologies & null\\
LaborieRSV18 \href{https://doi.org/10.1007/s10601-018-9281-x}{LaborieRSV18} & P. Laborie, J. Rogerie, P. Shaw, P. Vil{\'{\i}}m & {IBM} {ILOG} {CP} optimizer for scheduling - 20+ years of scheduling with constraints at {IBM/ILOG} & \href{articles/LaborieRSV18.pdf}{Yes} & \cite{LaborieRSV18} & 2018 & Constraints An Int. J. & 41\\
PourDERB18 \href{https://doi.org/10.1016/j.ejor.2017.08.033}{PourDERB18} & Shahrzad M. Pour, John H. Drake, Lena Secher Ejlertsen, Kourosh Marjani Rasmussen, Edmund K. Burke & A hybrid Constraint Programming/Mixed Integer Programming framework for the preventive signaling maintenance crew scheduling problem & \href{articles/PourDERB18.pdf}{Yes} & \cite{PourDERB18} & 2018 & Eur. J. Oper. Res. & 12\\
ShinBBHO18 \href{https://doi.org/10.1109/TSMC.2017.2681623}{ShinBBHO18} & Seung Yeob Shin, Y. Brun, H. Balasubramanian, Philip L. Henneman, Leon J. Osterweil & Discrete-Event Simulation and Integer Linear Programming for Constraint-Aware Resource Scheduling & \href{articles/ShinBBHO18.pdf}{Yes} & \cite{ShinBBHO18} & 2018 & {IEEE} Trans. Syst. Man Cybern. Syst. & 16\\
TangLWSK18 \href{https://doi.org/10.1111/mice.12277}{TangLWSK18} & Y. Tang, R. Liu, F. Wang, Q. Sun, Amr A. Kandil & Scheduling Optimization of Linear Schedule with Constraint Programming & No & \cite{TangLWSK18} & 2018 & Comput. Aided Civ. Infrastructure Eng. & 28\\
ZhangW18 \href{https://doi.org/10.1109/TEM.2017.2785774}{ZhangW18} & S. Zhang, S. Wang & Flexible Assembly Job-Shop Scheduling With Sequence-Dependent Setup Times and Part Sharing in a Dynamic Environment: Constraint Programming Model, Mixed-Integer Programming Model, and Dispatching Rules & \href{articles/ZhangW18.pdf}{Yes} & \cite{ZhangW18} & 2018 & {IEEE} Trans. Engineering Management & 18\\
KreterSS17 \href{https://doi.org/10.1007/s10601-016-9266-6}{KreterSS17} & S. Kreter, A. Schutt, Peter J. Stuckey & Using constraint programming for solving RCPSP/max-cal & \href{articles/KreterSS17.pdf}{Yes} & \cite{KreterSS17} & 2017 & Constraints An Int. J. & 31\\
NattafAL17 \href{https://doi.org/10.1007/s10601-017-9271-4}{NattafAL17} & M. Nattaf, C. Artigues, P. Lopez & Cumulative scheduling with variable task profiles and concave piecewise linear processing rate functions & \href{articles/NattafAL17.pdf}{Yes} & \cite{NattafAL17} & 2017 & Constraints An Int. J. & 18\\
Bonfietti16 \href{https://doi.org/10.3233/IA-160095}{Bonfietti16} & A. Bonfietti & A constraint programming scheduling solver for the MPOpt programming environment & No & \cite{Bonfietti16} & 2016 & Intelligenza Artificiale & 13\\
BridiBLMB16 \href{https://doi.org/10.1109/TPDS.2016.2516997}{BridiBLMB16} & T. Bridi, A. Bartolini, M. Lombardi, M. Milano, L. Benini & A Constraint Programming Scheduler for Heterogeneous High-Performance Computing Machines & \href{articles/BridiBLMB16.pdf}{Yes} & \cite{BridiBLMB16} & 2016 & {IEEE} Trans. Parallel Distributed Syst. & 14\\
DoulabiRP16 \href{https://doi.org/10.1287/ijoc.2015.0686}{DoulabiRP16} & Seyed Hossein Hashemi Doulabi, L. Rousseau, G. Pesant & A Constraint-Programming-Based Branch-and-Price-and-Cut Approach for Operating Room Planning and Scheduling & No & \cite{DoulabiRP16} & 2016 & {INFORMS} J. Comput. & 17\\
NovaraNH16 \href{https://doi.org/10.1016/j.compchemeng.2016.04.030}{NovaraNH16} & Franco M. Novara, Juan M. Novas, Gabriela P. Henning & A novel constraint programming model for large-scale scheduling problems in multiproduct multistage batch plants: Limited resources and campaign-based operation & \href{articles/NovaraNH16.pdf}{Yes} & \cite{NovaraNH16} & 2016 & Comput. Chem. Eng. & 17\\
ZarandiKS16 \href{https://doi.org/10.1007/s10845-013-0860-9}{ZarandiKS16} & M. H. Fazel Zarandi, H. Khorshidian, Mohsen Akbarpour Shirazi & A constraint programming model for the scheduling of {JIT} cross-docking systems with preemption & \href{articles/ZarandiKS16.pdf}{Yes} & \cite{ZarandiKS16} & 2016 & J. Intell. Manuf. & 17\\
EvenSH15a \href{http://arxiv.org/abs/1505.02487}{EvenSH15a} & C. Even, A. Schutt, Pascal Van Hentenryck & A Constraint Programming Approach for Non-Preemptive Evacuation Scheduling & \href{articles/EvenSH15a.pdf}{Yes} & \cite{EvenSH15a} & 2015 & CoRR & 16\\
GoelSHFS15 \href{https://doi.org/10.1016/j.ejor.2014.09.048}{GoelSHFS15} & V. Goel, M. Slusky, Willem{-}Jan van Hoeve, Kevin C. Furman, Y. Shao & Constraint programming for {LNG} ship scheduling and inventory management & \href{articles/GoelSHFS15.pdf}{Yes} & \cite{GoelSHFS15} & 2015 & Eur. J. Oper. Res. & 12\\
Kameugne15 \href{https://doi.org/10.1007/s10601-015-9227-5}{Kameugne15} & R. Kameugne & Propagation techniques of resource constraint for cumulative scheduling & \href{articles/Kameugne15.pdf}{Yes} & \cite{Kameugne15} & 2015 & Constraints An Int. J. & 2\\
LetortCB15 \href{https://doi.org/10.1007/s10601-014-9172-8}{LetortCB15} & A. Letort, M. Carlsson, N. Beldiceanu & Synchronized sweep algorithms for scalable scheduling constraints & \href{articles/LetortCB15.pdf}{Yes} & \cite{LetortCB15} & 2015 & Constraints An Int. J. & 52\\
NattafAL15 \href{https://doi.org/10.1007/s10601-015-9192-z}{NattafAL15} & M. Nattaf, C. Artigues, P. Lopez & A hybrid exact method for a scheduling problem with a continuous resource and energy constraints & \href{articles/NattafAL15.pdf}{Yes} & \cite{NattafAL15} & 2015 & Constraints An Int. J. & 21\\
Siala15 \href{https://doi.org/10.1007/s10601-015-9213-y}{Siala15} & M. Siala & Search, propagation, and learning in sequencing and scheduling problems & \href{articles/Siala15.pdf}{Yes} & \cite{Siala15} & 2015 & Constraints An Int. J. & 2\\
SimoninAHL15 \href{https://doi.org/10.1007/s10601-014-9169-3}{SimoninAHL15} & G. Simonin, C. Artigues, E. Hebrard, P. Lopez & Scheduling scientific experiments for comet exploration & \href{articles/SimoninAHL15.pdf}{Yes} & \cite{SimoninAHL15} & 2015 & Constraints An Int. J. & 23\\
WangMD15 \href{https://doi.org/10.1016/j.ejor.2015.06.008}{WangMD15} & T. Wang, N. Meskens, D. Duvivier & Scheduling operating theatres: Mixed integer programming vs. constraint programming & \href{articles/WangMD15.pdf}{Yes} & \cite{WangMD15} & 2015 & Eur. J. Oper. Res. & 13\\
BonfiettiLBM14 \href{https://doi.org/10.1016/j.artint.2013.09.006}{BonfiettiLBM14} & A. Bonfietti, M. Lombardi, L. Benini, M. Milano & {CROSS} cyclic resource-constrained scheduling solver & \href{articles/BonfiettiLBM14.pdf}{Yes} & \cite{BonfiettiLBM14} & 2014 & Artif. Intell. & 28\\
GrimesIOS14 \href{https://doi.org/10.1016/j.suscom.2014.08.009}{GrimesIOS14} & D. Grimes, G. Ifrim, B. O'Sullivan, H. Simonis & Analyzing the impact of electricity price forecasting on energy cost-aware scheduling & \href{articles/GrimesIOS14.pdf}{Yes} & \cite{GrimesIOS14} & 2014 & Sustain. Comput. Informatics Syst. & 16\\
KameugneFSN14 \href{https://doi.org/10.1007/s10601-013-9157-z}{KameugneFSN14} & R. Kameugne, Laure Pauline Fotso, Joseph D. Scott, Y. Ngo{-}Kateu & A quadratic edge-finding filtering algorithm for cumulative resource constraints & \href{articles/KameugneFSN14.pdf}{Yes} & \cite{KameugneFSN14} & 2014 & Constraints An Int. J. & 27\\
NovasH14 \href{https://doi.org/10.1016/j.eswa.2013.09.026}{NovasH14} & Juan M. Novas, Gabriela P. Henning & Integrated scheduling of resource-constrained flexible manufacturing systems using constraint programming & \href{articles/NovasH14.pdf}{Yes} & \cite{NovasH14} & 2014 & Expert Syst. Appl. & 14\\
BegB13 \href{http://doi.acm.org/10.1145/2512470}{BegB13} & Mirza Omer Beg, Peter van Beek & A constraint programming approach for integrated spatial and temporal scheduling for clustered architectures & No & \cite{BegB13} & 2013 & {ACM} Trans. Embed. Comput. Syst. & 23\\
HeinzSB13 \href{https://doi.org/10.1007/s10601-012-9136-9}{HeinzSB13} & S. Heinz, J. Schulz, J. Christopher Beck & Using dual presolving reductions to reformulate cumulative constraints & \href{articles/HeinzSB13.pdf}{Yes} & \cite{HeinzSB13} & 2013 & Constraints An Int. J. & 36\\
OzturkTHO13 \href{https://doi.org/10.1007/s10601-013-9142-6}{OzturkTHO13} & C. {\"{O}}zt{\"{u}}rk, S. Tunali, B. Hnich, M. Arslan Ornek & Balancing and scheduling of flexible mixed model assembly lines & \href{articles/OzturkTHO13.pdf}{Yes} & \cite{OzturkTHO13} & 2013 & Constraints An Int. J. & 36\\
HeinzSSW12 \href{https://doi.org/10.1007/s10601-011-9113-8}{HeinzSSW12} & S. Heinz, T. Schlechte, R. Stephan, M. Winkler & Solving steel mill slab design problems & \href{articles/HeinzSSW12.pdf}{Yes} & \cite{HeinzSSW12} & 2012 & Constraints An Int. J. & 12\\
LimtanyakulS12 \href{https://doi.org/10.1007/s10601-012-9118-y}{LimtanyakulS12} & K. Limtanyakul, U. Schwiegelshohn & Improvements of constraint programming and hybrid methods for scheduling of tests on vehicle prototypes & \href{articles/LimtanyakulS12.pdf}{Yes} & \cite{LimtanyakulS12} & 2012 & Constraints An Int. J. & 32\\
LombardiM12 \href{https://doi.org/10.1007/s10601-011-9115-6}{LombardiM12} & M. Lombardi, M. Milano & Optimal methods for resource allocation and scheduling: a cross-disciplinary survey & \href{articles/LombardiM12.pdf}{Yes} & \cite{LombardiM12} & 2012 & Constraints An Int. J. & 35\\
LombardiM12a \href{https://doi.org/10.1016/j.artint.2011.12.001}{LombardiM12a} & M. Lombardi, M. Milano & A min-flow algorithm for Minimal Critical Set detection in Resource Constrained Project Scheduling & \href{articles/LombardiM12a.pdf}{Yes} & \cite{LombardiM12a} & 2012 & Artif. Intell. & 10\\
NovasH12 \href{https://doi.org/10.1016/j.compchemeng.2012.01.005}{NovasH12} & Juan M. Novas, Gabriela P. Henning & A comprehensive constraint programming approach for the rolling horizon-based scheduling of automated wet-etch stations & \href{articles/NovasH12.pdf}{Yes} & \cite{NovasH12} & 2012 & Comput. Chem. Eng. & 17\\
BartakS11 \href{https://doi.org/10.1007/s10601-011-9109-4}{BartakS11} & R. Bart{\'{a}}k, Miguel A. Salido & Constraint satisfaction for planning and scheduling problems & \href{articles/BartakS11.pdf}{Yes} & \cite{BartakS11} & 2011 & Constraints An Int. J. & 5\\
BeckFW11 \href{https://doi.org/10.1287/ijoc.1100.0388}{BeckFW11} & J. Christopher Beck, T. K. Feng, J. Watson & Combining Constraint Programming and Local Search for Job-Shop Scheduling & No & \cite{BeckFW11} & 2011 & {INFORMS} J. Comput. & 14\\
BeldiceanuCDP11 \href{https://doi.org/10.1007/s10479-010-0731-0}{BeldiceanuCDP11} & N. Beldiceanu, M. Carlsson, S. Demassey, E. Poder & New filtering for the \emph{cumulative} constraint in the context of non-overlapping rectangles & \href{articles/BeldiceanuCDP11.pdf}{Yes} & \cite{BeldiceanuCDP11} & 2011 & Ann. Oper. Res. & 24\\
BeniniLMR11 \href{https://doi.org/10.1007/s10479-010-0718-x}{BeniniLMR11} & L. Benini, M. Lombardi, M. Milano, M. Ruggiero & Optimal resource allocation and scheduling for the {CELL} {BE} platform & \href{articles/BeniniLMR11.pdf}{Yes} & \cite{BeniniLMR11} & 2011 & Ann. Oper. Res. & 27\\
HachemiGR11 \href{https://doi.org/10.1007/s10479-010-0698-x}{HachemiGR11} & Nizar El Hachemi, M. Gendreau, L. Rousseau & A hybrid constraint programming approach to the log-truck scheduling problem & \href{articles/HachemiGR11.pdf}{Yes} & \cite{HachemiGR11} & 2011 & Ann. Oper. Res. & 16\\
KelbelH11 \href{https://doi.org/10.1007/s10845-009-0318-2}{KelbelH11} & J. Kelbel, Z. Hanz{\'{a}}lek & Solving production scheduling with earliness/tardiness penalties by constraint programming & \href{articles/KelbelH11.pdf}{Yes} & \cite{KelbelH11} & 2011 & J. Intell. Manuf. & 10\\
KovacsB11 \href{https://doi.org/10.1007/s10601-009-9088-x}{KovacsB11} & A. Kov{\'{a}}cs, J. Christopher Beck & A global constraint for total weighted completion time for unary resources & \href{articles/KovacsB11.pdf}{Yes} & \cite{KovacsB11} & 2011 & Constraints An Int. J. & 24\\
KovacsK11 \href{https://doi.org/10.1007/s10601-010-9102-3}{KovacsK11} & A. Kov{\'{a}}cs, T. Kis & Constraint programming approach to a bilevel scheduling problem & \href{articles/KovacsK11.pdf}{Yes} & \cite{KovacsK11} & 2011 & Constraints An Int. J. & 24\\
SchausHMCMD11 \href{https://doi.org/10.1007/s10601-010-9100-5}{SchausHMCMD11} & P. Schaus, Pascal Van Hentenryck, J. Monette, C. Coffrin, L. Michel, Y. Deville & Solving Steel Mill Slab Problems with constraint-based techniques: CP, LNS, and {CBLS} & \href{articles/SchausHMCMD11.pdf}{Yes} & \cite{SchausHMCMD11} & 2011 & Constraints An Int. J. & 23\\
SchuttFSW11 \href{https://doi.org/10.1007/s10601-010-9103-2}{SchuttFSW11} & A. Schutt, T. Feydy, Peter J. Stuckey, Mark G. Wallace & Explaining the cumulative propagator & \href{articles/SchuttFSW11.pdf}{Yes} & \cite{SchuttFSW11} & 2011 & Constraints An Int. J. & 33\\
TopalogluO11 \href{https://doi.org/10.1016/j.cor.2010.04.018}{TopalogluO11} & S. Topaloglu, I. Ozkarahan & A constraint programming-based solution approach for medical resident scheduling problems & \href{articles/TopalogluO11.pdf}{Yes} & \cite{TopalogluO11} & 2011 & Comput. Oper. Res. & 10\\
TrojetHL11 \href{https://doi.org/10.1016/j.cie.2010.08.014}{TrojetHL11} & M. Trojet, F. H'Mida, P. Lopez & Project scheduling under resource constraints: Application of the cumulative global constraint in a decision support framework & \href{articles/TrojetHL11.pdf}{Yes} & \cite{TrojetHL11} & 2011 & Comput. Ind. Eng. & 7\\
BartakCS10 \href{https://doi.org/10.1007/s10479-008-0492-1}{BartakCS10} & R. Bart{\'{a}}k, O. Cepek, P. Surynek & Discovering implied constraints in precedence graphs with alternatives & \href{articles/BartakCS10.pdf}{Yes} & \cite{BartakCS10} & 2010 & Ann. Oper. Res. & 31\\
BartakSR10 \href{https://doi.org/10.1017/S0269888910000202}{BartakSR10} & R. Bart{\'{a}}k, Miguel A. Salido, F. Rossi & New trends in constraint satisfaction, planning, and scheduling: a survey & \href{articles/BartakSR10.pdf}{Yes} & \cite{BartakSR10} & 2010 & Knowl. Eng. Rev. & 31\\
LombardiM10a \href{https://doi.org/10.1016/j.artint.2010.02.004}{LombardiM10a} & M. Lombardi, M. Milano & Allocation and scheduling of Conditional Task Graphs & \href{articles/LombardiM10a.pdf}{Yes} & \cite{LombardiM10a} & 2010 & Artif. Intell. & 30\\
LopesCSM10 \href{https://doi.org/10.1007/s10601-009-9086-z}{LopesCSM10} & Tony Minoru Tamura Lopes, Andr{\'{e}} A. Cir{\'{e}}, Cid Carvalho de Souza, Arnaldo Vieira Moura & A hybrid model for a multiproduct pipeline planning and scheduling problem & \href{articles/LopesCSM10.pdf}{Yes} & \cite{LopesCSM10} & 2010 & Constraints An Int. J. & 39\\
NovasH10 \href{https://doi.org/10.1016/j.compchemeng.2010.07.011}{NovasH10} & Juan M. Novas, Gabriela P. Henning & Reactive scheduling framework based on domain knowledge and constraint programming & \href{articles/NovasH10.pdf}{Yes} & \cite{NovasH10} & 2010 & Comput. Chem. Eng. & 20\\
ZeballosQH10 \href{https://doi.org/10.1016/j.engappai.2009.07.002}{ZeballosQH10} & L. Zeballos, O. Quiroga, Gabriela P. Henning & A constraint programming model for the scheduling of flexible manufacturing systems with machine and tool limitations & \href{articles/ZeballosQH10.pdf}{Yes} & \cite{ZeballosQH10} & 2010 & Eng. Appl. Artif. Intell. & 20\\
BocewiczBB09 \href{https://doi.org/10.1504/IJIIDS.2009.023038}{BocewiczBB09} & G. Bocewicz, I. Bach, Zbigniew Antoni Banaszak & Logic-algebraic method based and constraints programming driven approach to AGVs scheduling & No & \cite{BocewiczBB09} & 2009 & Int. J. Intell. Inf. Database Syst. & 19\\
GarridoAO09 \href{https://doi.org/10.1007/s10951-008-0083-7}{GarridoAO09} & A. Garrido, M. Arang{\'{u}}, E. Onaindia & A constraint programming formulation for planning: from plan scheduling to plan generation & \href{articles/GarridoAO09.pdf}{Yes} & \cite{GarridoAO09} & 2009 & J. Sched. & 30\\
RuggieroBBMA09 \href{https://doi.org/10.1109/TCAD.2009.2013536}{RuggieroBBMA09} & M. Ruggiero, D. Bertozzi, L. Benini, M. Milano, A. Andrei & Reducing the Abstraction and Optimality Gaps in the Allocation and Scheduling for Variable Voltage/Frequency MPSoC Platforms & \href{articles/RuggieroBBMA09.pdf}{Yes} & \cite{RuggieroBBMA09} & 2009 & {IEEE} Trans. Comput. Aided Des. Integr. Circuits Syst. & 14\\
abs-0907-0939 \href{http://arxiv.org/abs/0907.0939}{abs-0907-0939} & T. Petit, E. Poder & The Soft Cumulative Constraint & \href{articles/abs-0907-0939.pdf}{Yes} & \cite{abs-0907-0939} & 2009 & CoRR & 12\\
GarridoOS08 \href{https://doi.org/10.1016/j.engappai.2008.03.009}{GarridoOS08} & A. Garrido, E. Onaindia, {\'{O}}scar Sapena & Planning and scheduling in an e-learning environment. {A} constraint-programming-based approach & \href{articles/GarridoOS08.pdf}{Yes} & \cite{GarridoOS08} & 2008 & Eng. Appl. Artif. Intell. & 11\\
KovacsB08 \href{https://doi.org/10.1016/j.engappai.2008.03.004}{KovacsB08} & A. Kov{\'{a}}cs, J. Christopher Beck & A global constraint for total weighted completion time for cumulative resources & \href{articles/KovacsB08.pdf}{Yes} & \cite{KovacsB08} & 2008 & Eng. Appl. Artif. Intell. & 7\\
LiessM08 \href{https://doi.org/10.1007/s10479-007-0188-y}{LiessM08} & O. Liess, P. Michelon & A constraint programming approach for the resource-constrained project scheduling problem & \href{articles/LiessM08.pdf}{Yes} & \cite{LiessM08} & 2008 & Ann. Oper. Res. & 12\\
MalikMB08 \href{https://doi.org/10.1142/S0218213008003765}{MalikMB08} & Abid M. Malik, J. McInnes, Peter van Beek & Optimal Basic Block Instruction Scheduling for Multiple-Issue Processors Using Constraint Programming & No & \cite{MalikMB08} & 2008 & Int. J. Artif. Intell. Tools & 18\\
Simonis07 \href{https://doi.org/10.1007/s10601-006-9011-7}{Simonis07} & H. Simonis & Models for Global Constraint Applications & \href{articles/Simonis07.pdf}{Yes} & \cite{Simonis07} & 2007 & Constraints An Int. J. & 30\\
Hooker06 \href{https://doi.org/10.1007/s10601-006-8060-2}{Hooker06} & John N. Hooker & An Integrated Method for Planning and Scheduling to Minimize Tardiness & \href{articles/Hooker06.pdf}{Yes} & \cite{Hooker06} & 2006 & Constraints An Int. J. & 19\\
KhayatLR06 \href{https://doi.org/10.1016/j.ejor.2005.02.077}{KhayatLR06} & Ghada El Khayat, A. Langevin, D. Riopel & Integrated production and material handling scheduling using mathematical programming and constraint programming & \href{articles/KhayatLR06.pdf}{Yes} & \cite{KhayatLR06} & 2006 & Eur. J. Oper. Res. & 15\\
SadykovW06 \href{https://doi.org/10.1287/ijoc.1040.0110}{SadykovW06} & R. Sadykov, Laurence A. Wolsey & Integer Programming and Constraint Programming in Solving a Multimachine Assignment Scheduling Problem with Deadlines and Release Dates & No & \cite{SadykovW06} & 2006 & {INFORMS} J. Comput. & 9\\
SureshMOK06 \href{https://doi.org/10.1080/17445760600567842}{SureshMOK06} & S. Sundaram, V. Mani, S. N. Omkar, H. J. Kim & Divisible load scheduling in distributed system with buffer constraints: genetic algorithm and linear programming approach & No & \cite{SureshMOK06} & 2006 & Int. J. Parallel Emergent Distributed Syst. & 19\\
Hooker05 \href{https://doi.org/10.1007/s10601-005-2812-2}{Hooker05} & John N. Hooker & A Hybrid Method for the Planning and Scheduling & \href{articles/Hooker05.pdf}{Yes} & \cite{Hooker05} & 2005 & Constraints An Int. J. & 17\\
VilimBC05 \href{https://doi.org/10.1007/s10601-005-2814-0}{VilimBC05} & P. Vil{\'{\i}}m, R. Bart{\'{a}}k, O. Cepek & Extension of \emph{O}(\emph{n} log \emph{n}) Filtering Algorithms for the Unary Resource Constraint to Optional Activities & \href{articles/VilimBC05.pdf}{Yes} & \cite{VilimBC05} & 2005 & Constraints An Int. J. & 23\\
ZeballosH05 \href{http://journal.iberamia.org/index.php/ia/article/view/452/article\%20\%281\%29.pdf}{ZeballosH05} & L. Zeballos, Gabriela P. Henning & A Constraint Programming Approach to {FMS} Scheduling. Consideration of Storage and Transportation Resources & \href{articles/ZeballosH05.pdf}{Yes} & \cite{ZeballosH05} & 2005 & Inteligencia Artif. & 10\\
PoderBS04 \href{https://doi.org/10.1016/S0377-2217(02)00756-7}{PoderBS04} & E. Poder, N. Beldiceanu, E. Sanlaville & Computing a lower approximation of the compulsory part of a task with varying duration and varying resource consumption & \href{articles/PoderBS04.pdf}{Yes} & \cite{PoderBS04} & 2004 & Eur. J. Oper. Res. & 16\\
KuchcinskiW03 \href{https://doi.org/10.1016/S1383-7621(03)00075-4}{KuchcinskiW03} & K. Kuchcinski, C. Wolinski & Global approach to assignment and scheduling of complex behaviors based on {HCDG} and constraint programming & \href{articles/KuchcinskiW03.pdf}{Yes} & \cite{KuchcinskiW03} & 2003 & J. Syst. Archit. & 15\\
Tsang03 \href{https://doi.org/10.1023/A:1024016929283}{Tsang03} & Edward P. K. Tsang & Constraint Based Scheduling: Applying Constraint Programming to Scheduling Problems & \href{articles/Tsang03.pdf}{Yes} & \cite{Tsang03} & 2003 & J. Sched. & 2\\
LorigeonBB02 \href{https://doi.org/10.1057/palgrave.jors.2601421}{LorigeonBB02} & T. Lorigeon, J. Billaut, J. Bouquard & A dynamic programming algorithm for scheduling jobs in a two-machine open shop with an availability constraint & No & \cite{LorigeonBB02} & 2002 & J. Oper. Res. Soc. & 8\\
Timpe02 \href{https://doi.org/10.1007/s00291-002-0107-1}{Timpe02} & C. Timpe & Solving planning and scheduling problems with combined integer and constraint programming & \href{articles/Timpe02.pdf}{Yes} & \cite{Timpe02} & 2002 & {OR} Spectr. & 18\\
MartinPY01 \href{https://doi.org/10.1023/A:1016067230126}{MartinPY01} & F. Martin, A. Pinkney, X. Yu & Cane Railway Scheduling via Constraint Logic Programming: Labelling Order and Constraints in a Real-Life Application & \href{articles/MartinPY01.pdf}{Yes} & \cite{MartinPY01} & 2001 & Ann. Oper. Res. & 17\\
Mason01 \href{https://doi.org/10.1023/A:1016023415105}{Mason01} & Andrew J. Mason & Elastic Constraint Branching, the Wedelin/Carmen Lagrangian Heuristic and Integer Programming for Personnel Scheduling & \href{articles/Mason01.pdf}{Yes} & \cite{Mason01} & 2001 & Ann. Oper. Res. & 38\\
ArtiguesR00 \href{https://doi.org/10.1016/S0377-2217(99)00496-8}{ArtiguesR00} & C. Artigues, F. Roubellat & A polynomial activity insertion algorithm in a multi-resource schedule with cumulative constraints and multiple modes & \href{articles/ArtiguesR00.pdf}{Yes} & \cite{ArtiguesR00} & 2000 & Eur. J. Oper. Res. & 20\\
BaptisteP00 \href{https://doi.org/10.1023/A:1009822502231}{BaptisteP00} & P. Baptiste, Claude Le Pape & Constraint Propagation and Decomposition Techniques for Highly Disjunctive and Highly Cumulative Project Scheduling Problems & \href{articles/BaptisteP00.pdf}{Yes} & \cite{BaptisteP00} & 2000 & Constraints An Int. J. & 21\\
HeipckeCCS00 \href{https://doi.org/10.1023/A:1009860311452}{HeipckeCCS00} & S. Heipcke, Y. Colombani, Cristina C. B. Cavalcante, Cid C. de Souza & Scheduling under Labour Resource Constraints & \href{articles/HeipckeCCS00.pdf}{Yes} & \cite{HeipckeCCS00} & 2000 & Constraints An Int. J. & 8\\
KorbaaYG00 \href{https://doi.org/10.1016/S0947-3580(00)71113-7}{KorbaaYG00} & O. Korbaa, P. Yim, J. Gentina & Solving Transient Scheduling Problems with Constraint Programming & \href{articles/KorbaaYG00.pdf}{Yes} & \cite{KorbaaYG00} & 2000 & Eur. J. Control & 10\\
LopezAKYG00 \href{https://doi.org/10.1016/S0947-3580(00)71114-9}{LopezAKYG00} & P. Lopez, H. Alla, O. Korbaa, P. Yim, J. Gentina & Discussion on: 'Solving Transient Scheduling Problems with Constraint Programming' by O. Korbaa, P. Yim, and {J.-C.} Gentina & \href{articles/LopezAKYG00.pdf}{Yes} & \cite{LopezAKYG00} & 2000 & Eur. J. Control & 4\\
SakkoutW00 \href{https://doi.org/10.1023/A:1009856210543}{SakkoutW00} & Hani El Sakkout, M. Wallace & Probe Backtrack Search for Minimal Perturbation in Dynamic Scheduling & \href{articles/SakkoutW00.pdf}{Yes} & \cite{SakkoutW00} & 2000 & Constraints An Int. J. & 30\\
SchildW00 \href{https://doi.org/10.1023/A:1009804226473}{SchildW00} & K. Schild, J. W{\"{u}}rtz & Scheduling of Time-Triggered Real-Time Systems & \href{articles/SchildW00.pdf}{Yes} & \cite{SchildW00} & 2000 & Constraints An Int. J. & 23\\
SourdN00 \href{https://doi.org/10.1287/ijoc.12.4.341.11881}{SourdN00} & F. Sourd, W. Nuijten & Multiple-Machine Lower Bounds for Shop-Scheduling Problems & No & \cite{SourdN00} & 2000 & {INFORMS} J. Comput. & 12\\
BensanaLV99 \href{https://doi.org/10.1023/A:1026488509554}{BensanaLV99} & E. Bensana, M. Lema{\^{\i}}tre, G. Verfaillie & Earth Observation Satellite Management & \href{articles/BensanaLV99.pdf}{Yes} & \cite{BensanaLV99} & 1999 & Constraints An Int. J. & 7\\
BelhadjiI98 \href{https://doi.org/10.1023/A:1009777711218}{BelhadjiI98} & S. Belhadji, A. Isli & Temporal Constraint Satisfaction Techniques in Job Shop Scheduling Problem Solving & \href{articles/BelhadjiI98.pdf}{Yes} & \cite{BelhadjiI98} & 1998 & Constraints An Int. J. & 9\\
NuijtenP98 \href{https://doi.org/10.1023/A:1009687210594}{NuijtenP98} & W. Nuijten, Claude Le Pape & Constraint-Based Job Shop Scheduling with {\textbackslash}sc Ilog Scheduler & \href{articles/NuijtenP98.pdf}{Yes} & \cite{NuijtenP98} & 1998 & J. Heuristics & 16\\
PapaB98 \href{https://doi.org/10.1023/A:1009723704757}{PapaB98} & Claude Le Pape, P. Baptiste & Resource Constraints for Preemptive Job-shop Scheduling & \href{articles/PapaB98.pdf}{Yes} & \cite{PapaB98} & 1998 & Constraints An Int. J. & 25\\
Darby-DowmanLMZ97 \href{https://doi.org/10.1007/BF00137871}{Darby-DowmanLMZ97} & K. Darby{-}Dowman, J. Little, G. Mitra, M. Zaffalon & Constraint Logic Programming and Integer Programming Approaches and Their Collaboration in Solving an Assignment Scheduling Problem & \href{articles/Darby-DowmanLMZ97.pdf}{Yes} & \cite{Darby-DowmanLMZ97} & 1997 & Constraints An Int. J. & 20\\
FalaschiGMP97 \href{https://doi.org/10.1006/inco.1997.2638}{FalaschiGMP97} & M. Falaschi, M. Gabbrielli, K. Marriott, C. Palamidessi & Constraint Logic Programming with Dynamic Scheduling: {A} Semantics Based on Closure Operators & \href{articles/FalaschiGMP97.pdf}{Yes} & \cite{FalaschiGMP97} & 1997 & Inf. Comput. & 27\\
LammaMM97 \href{https://doi.org/10.1016/S0954-1810(96)00002-7}{LammaMM97} & E. Lamma, P. Mello, M. Milano & A distributed constraint-based scheduler & \href{articles/LammaMM97.pdf}{Yes} & \cite{LammaMM97} & 1997 & Artif. Intell. Eng. & 15\\
Zhou97 \href{https://doi.org/10.1023/A:1009757726572}{Zhou97} & J. Zhou & A Permutation-Based Approach for Solving the Job-Shop Problem & \href{articles/Zhou97.pdf}{Yes} & \cite{Zhou97} & 1997 & Constraints An Int. J. & 29\\
Wallace96 \href{https://doi.org/10.1007/BF00143881}{Wallace96} & M. Wallace & Practical Applications of Constraint Programming & \href{articles/Wallace96.pdf}{Yes} & \cite{Wallace96} & 1996 & Constraints An Int. J. & 30\\
AggounB93 \href{https://www.sciencedirect.com/science/article/pii/089571779390068A}{AggounB93} & A. Aggoun, N. Beldiceanu & Extending {CHIP} in order to solve complex scheduling and placement problems & \href{articles/AggounB93.pdf}{Yes} & \cite{AggounB93} & 1993 & Mathematical and Computer Modelling & 17\\
Tay92 \href{}{Tay92} & David B. H. Tay & {COPS:} {A} Constraint Programming Approach to Resource-Limited Project Scheduling & No & \cite{Tay92} & 1992 & Comput. J. & null\\
DincbasSH90 \href{https://doi.org/10.1016/0743-1066(90)90052-7}{DincbasSH90} & M. Dincbas, H. Simonis, Pascal Van Hentenryck & Solving Large Combinatorial Problems in Logic Programming & \href{articles/DincbasSH90.pdf}{Yes} & \cite{DincbasSH90} & 1990 & J. Log. Program. & 19\\
\end{longtable}
}

