{\scriptsize
\begin{longtable}{llp{5cm}p{10cm}rp{3cm}l}
\caption{Article without Local Copy}\\ \toprule
Key & URL & Authors & Title & Year & \shortstack{Conference\\/Journal} & Cite\\ \midrule
\endhead
\bottomrule
\endfoot
AbreuNP23 & \href{https://doi.org/10.1080/00207543.2022.2154404}{AbreuNP23} & Levi Ribeiro de Abreu and Marcelo Seido Nagano and Bruno A. Prata & A new two-stage constraint programming approach for open shop scheduling problem with machine blocking & 2023 & Int. J. Prod. Res. & \cite{AbreuNP23}\\ShaikhK23 & \href{https://doi.org/10.1504/IJESDF.2023.10045616}{ShaikhK23} & Aftab Ahmed Shaikh and Abdullah Ayub Khan & Management of electronic ledger: a constraint programming approach for solving curricula scheduling problems & 2023 & Int. J. Electron. Secur. Digit. Forensics & \cite{ShaikhK23}\\FarsiTM22 & \href{https://api.semanticscholar.org/CorpusID:250301745}{FarsiTM22} & Azadeh Farsi and S. Ali Torabi and Mahdi Mokhtarzadeh & Integrated surgery scheduling by constraint programming and meta-heuristics & 2022 & International Journal of Management Science and Engineering Management & \cite{FarsiTM22}\\Fatemi-AnarakiMFN22 & \href{https://api.semanticscholar.org/CorpusID:252524295}{Fatemi-AnarakiMFN22} & Soroush Fatemi-Anaraki and Reza Tavakkoli-Moghaddam and Mehdi Foumani and Behdin Vahedi-Nouri & Scheduling of Multi-Robot Job Shop Systems in Dynamic Environments: Mixed-Integer Linear Programming and Constraint Programming Approaches & 2022 & Omega & \cite{Fatemi-AnarakiMFN22}\\ShiYXQ22 & \href{https://doi.org/10.1080/00207543.2021.1963496}{ShiYXQ22} & Ganquan Shi and Zhouwang Yang and Yang Xu and Yuchen Quan & Solving the integrated process planning and scheduling problem using an enhanced constraint programming-based approach & 2022 & Int. J. Prod. Res. & \cite{ShiYXQ22}\\YunusogluY22 & \href{https://doi.org/10.1080/00207543.2021.1885068}{YunusogluY22} & Pinar Yunusoglu and Seyda Topaloglu Yildiz & Constraint programming approach for multi-resource-constrained unrelated parallel machine scheduling problem with sequence-dependent setup times & 2022 & Int. J. Prod. Res. & \cite{YunusogluY22}\\AbreuAPNM21 & \href{https://api.semanticscholar.org/CorpusID:238794651}{AbreuAPNM21} & Levi Ribeiro de Abreu and Kennedy A. G. Ara{\'u}jo and Bruno de Athayde Prata and Marcelo Seido Nagano and J. V. Moccellin & A new variable neighbourhood search with a constraint programming search strategy for the open shop scheduling problem with operation repetitions & 2021 & Engineering Optimization & \cite{AbreuAPNM21}\\AlizdehS20 & \href{https://doi.org/10.1504/IJAIP.2020.106687}{AlizdehS20} & Samira Alizdeh and Shahram Saeidi & Fuzzy project scheduling with critical path including risk and resource constraints using linear programming & 2020 & Int. J. Adv. Intell. Paradigms & \cite{AlizdehS20}\\BadicaBI20 & \href{https://doi.org/10.3233/AIC-200650}{BadicaBI20} & Amelia Badica and Costin Badica and Mirjana Ivanovic & Block structured scheduling using constraint logic programming & 2020 & {AI} Commun. & \cite{BadicaBI20}\\FallahiAC20 & \href{https://api.semanticscholar.org/CorpusID:213449737}{FallahiAC20} & Abdellah El Fallahi and El Yaakoubi Anass and Mohammad Cherkaoui & Tabu search and constraint programming-based approach for a real scheduling and routing problem & 2020 & International Journal of Applied Management Science & \cite{FallahiAC20}\\MokhtarzadehTNF20 & \href{https://doi.org/10.1080/0951192X.2020.1736713}{MokhtarzadehTNF20} & Mahdi Mokhtarzadeh and Reza Tavakkoli{-}Moghaddam and Behdin Vahedi Nouri and Azadeh Farsi & Scheduling of human-robot collaboration in assembly of printed circuit boards: a constraint programming approach & 2020 & Int. J. Comput. Integr. Manuf. & \cite{MokhtarzadehTNF20}\\Polo-MejiaALB20 & \href{https://doi.org/10.1080/00207543.2019.1693654}{Polo-MejiaALB20} & Oliver Polo{-}Mej{\'{\i}}a and Christian Artigues and Pierre Lopez and Virginie Basini & Mixed-integer/linear and constraint programming approaches for activity scheduling in a nuclear research facility & 2020 & Int. J. Prod. Res. & \cite{Polo-MejiaALB20}\\ZouZ20 & \href{https://api.semanticscholar.org/CorpusID:208840808}{ZouZ20} & Xin Zou and Lihui Zhang & A constraint programming approach for scheduling repetitive projects with atypical activities considering soft logic & 2020 & Automation in Construction & \cite{ZouZ20}\\NishikawaSTT19 & \href{http://www.ijnc.org/index.php/ijnc/article/view/201}{NishikawaSTT19} & Hiroki Nishikawa and Kana Shimada and Ittetsu Taniguchi and Hiroyuki Tomiyama & A Constraint Programming Approach to Scheduling of Malleable Tasks & 2019 & Int. J. Netw. Comput. & \cite{NishikawaSTT19}\\YounespourAKE19 & \href{https://api.semanticscholar.org/CorpusID:208103305}{YounespourAKE19} & Maryam Younespour and Arezoo Atighehchian and Kamran Kianfar and Ehsan Tarkesh Esfahani & Using mixed integer programming and constraint programming for operating rooms scheduling with modified block strategy & 2019 & Operations research for health care & \cite{YounespourAKE19}\\GokgurHO18 & \href{https://doi.org/10.1080/00207543.2017.1421781}{GokgurHO18} & Burak G{\"{o}}kg{\"{u}}r and Brahim Hnich and Selin {\"{O}}zpeynirci & Parallel machine scheduling with tool loading: a constraint programming approach & 2018 & Int. J. Prod. Res. & \cite{GokgurHO18}\\Ham18 & \href{https://api.semanticscholar.org/CorpusID:116853255}{Ham18} & Andy Ham & Integrated scheduling of m-truck, m-drone, and m-depot constrained by time-window, drop-pickup, and m-visit using constraint programming & 2018 & Transportation Research Part C: Emerging Technologies & \cite{Ham18}\\TangLWSK18 & \href{https://doi.org/10.1111/mice.12277}{TangLWSK18} & Yuanjie Tang and Rengkui Liu and Futian Wang and Quanxin Sun and Amr A. Kandil & Scheduling Optimization of Linear Schedule with Constraint Programming & 2018 & Comput. Aided Civ. Infrastructure Eng. & \cite{TangLWSK18}\\Bonfietti16 & \href{https://doi.org/10.3233/IA-160095}{Bonfietti16} & Alessio Bonfietti & A constraint programming scheduling solver for the MPOpt programming environment & 2016 & Intelligenza Artificiale & \cite{Bonfietti16}\\DoulabiRP16 & \href{https://doi.org/10.1287/ijoc.2015.0686}{DoulabiRP16} & Seyed Hossein Hashemi Doulabi and Louis{-}Martin Rousseau and Gilles Pesant & A Constraint-Programming-Based Branch-and-Price-and-Cut Approach for Operating Room Planning and Scheduling & 2016 & {INFORMS} J. Comput. & \cite{DoulabiRP16}\\BegB13 & \href{http://doi.acm.org/10.1145/2512470}{BegB13} & Mirza Omer Beg and Peter van Beek & A constraint programming approach for integrated spatial and temporal scheduling for clustered architectures & 2013 & {ACM} Trans. Embed. Comput. Syst. & \cite{BegB13}\\BeckFW11 & \href{https://doi.org/10.1287/ijoc.1100.0388}{BeckFW11} & J. Christopher Beck and T. K. Feng and Jean{-}Paul Watson & Combining Constraint Programming and Local Search for Job-Shop Scheduling & 2011 & {INFORMS} J. Comput. & \cite{BeckFW11}\\BocewiczBB09 & \href{https://doi.org/10.1504/IJIIDS.2009.023038}{BocewiczBB09} & Grzegorz Bocewicz and Irena Bach and Zbigniew Antoni Banaszak & Logic-algebraic method based and constraints programming driven approach to AGVs scheduling & 2009 & Int. J. Intell. Inf. Database Syst. & \cite{BocewiczBB09}\\MalikMB08 & \href{https://doi.org/10.1142/S0218213008003765}{MalikMB08} & Abid M. Malik and Jim McInnes and Peter van Beek & Optimal Basic Block Instruction Scheduling for Multiple-Issue Processors Using Constraint Programming & 2008 & Int. J. Artif. Intell. Tools & \cite{MalikMB08}\\SadykovW06 & \href{https://doi.org/10.1287/ijoc.1040.0110}{SadykovW06} & Ruslan Sadykov and Laurence A. Wolsey & Integer Programming and Constraint Programming in Solving a Multimachine Assignment Scheduling Problem with Deadlines and Release Dates & 2006 & {INFORMS} J. Comput. & \cite{SadykovW06}\\SureshMOK06 & \href{https://doi.org/10.1080/17445760600567842}{SureshMOK06} & Suresh Sundaram and V. Mani and S. N. Omkar and H. J. Kim & Divisible load scheduling in distributed system with buffer constraints: genetic algorithm and linear programming approach & 2006 & Int. J. Parallel Emergent Distributed Syst. & \cite{SureshMOK06}\\LorigeonBB02 & \href{https://doi.org/10.1057/palgrave.jors.2601421}{LorigeonBB02} & Thomas Lorigeon and Jean{-}Charles Billaut and Jean{-}Louis Bouquard & A dynamic programming algorithm for scheduling jobs in a two-machine open shop with an availability constraint & 2002 & J. Oper. Res. Soc. & \cite{LorigeonBB02}\\SourdN00 & \href{https://doi.org/10.1287/ijoc.12.4.341.11881}{SourdN00} & Francis Sourd and Wim Nuijten & Multiple-Machine Lower Bounds for Shop-Scheduling Problems & 2000 & {INFORMS} J. Comput. & \cite{SourdN00}\\Tay92 & \href{}{Tay92} & David B. H. Tay & {COPS:} {A} Constraint Programming Approach to Resource-Limited Project Scheduling & 1992 & Comput. J. & \cite{Tay92}\\\end{longtable}
}

